Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-14 paper/ms.tex
update ms
Check <5% BANYAN probabilities

We performed an independent search for strongly periodic phenomena
using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
the PDC\_SAP light curves, we normalized each light curve, and then
re-binned it into equal width bins {\bf LB: how long?} to account for
the uneven spacing in the TESS data, as well as the data gap during
each sector caused by satellite downlink.  We then padded the data to
ensure that the light curve had a length that was a power of two, as
described by \citeauthor{2019ApJ...876..127Z}.  We then took the
Fourier transform of the corrected, padded light curve using {\tt
numpy.fft.fft} and searched for peaks with a significance of over
12-$\sigma$ within each set of 500 bins.

@@

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CQVs.  The objects are sorted first in order of the number of
TESS 120-second cadence sectors in which they clearly demonstrated the
CQV phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CQVs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.  Regarding likely astrometric
or visual binaries, \ngoodhighruwe/\ngoods\ high-quality CQVs have a
Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
share this characteristic.\footnote{For an explanation of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php? id=3757412}.  Elevated RUWEs imply elevated noise relative to a single-source astrometric model, which can be caused by marginally resolved point sources, astrophysical photometric variability, or astrophysical astrometric motion.}

@@

Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster using
BANYAN\,$\Sigma$.  The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality and youth of that group.  The yield
in Sco-Cen is not surprising, since Sco-Cen contains the majority of
pre-main-sequence stars in the solar neighborhood, any many of its stars
were selected for TESS 120-second cadence observations by various
guest investigators.  Given the
$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
be many more CQVs in Sco-Cen that remain to be discovered.

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Bonafide, candidate, and debunked complex quasiperiodic
  variables from the TESS 2-minute data. {\bf For internal
  review, full versions are available here
  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
%\toprule
%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
%\midrule
%\endhead
\startdata
TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
-- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
  flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
  \ndebunked\ impostors (\texttt{Quality} flag -1).  The
  machine-readable version, available online, includes additional
  columns for the Gaia DR2 source identifiers and parameter
  uncertainties.  The age uncertainties are typically $\approx \pm
  10\%$, but can be asymmetric.  {\bf The median temperature, radius, and
  mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\%
  respectively}.  $N_{\rm sector}$ denotes the number of TESS sectors
  for which {\it any} data are expected to be acquired between July~2018 and
  Oct~2024.  This number is generally greater than the number of
  sectors for which 120-second cadence data exist.   Association names
  and provenance follow conventions adopted by
  \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	%APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
}
\end{deluxetable}
\clearpage

>>>>

We performed an independent search for strongly periodic phenomena
using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
the PDC\_SAP light curves, we normalized each light curve, and then
re-binned it into equal width 120-second bins to account for the
uneven spacing in the TESS data, as well as the data gap caused by
satellite downlink during each sector.  We then padded the data to
ensure that the light curve had a length that was a power of two, as
described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
transform of the corrected, padded light curve using {\tt
numpy.fft.fft}, we then searched for peaks with a significance of over
12-$\sigma$ within a set of 500 bins. 
{\bf LB: by the latter ``bins'', does this mean frequencies?}

@@

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CQVs.  The objects are sorted first in order of the number of
TESS 120-second cadence sectors in which they clearly demonstrated the
CQV phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CQVs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.  Regarding likely astrometric
or visual binaries, \ngoodhighruwe/\ngoods\ high-quality CQVs have a
Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
share this characteristic.\footnote{For an explanation of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php? id=3757412}.  Elevated RUWEs imply elevated noise relative to a single-source astrometric model. This can be caused by marginally resolved point sources, photometric variability, or astrometric motion.}

@@

Of our \ncqvsnodebunked\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster, primarily using
BANYAN\,$\Sigma$.\footnote{Two of the
	\nnotfieldbanyan\ memberships were made with low confidence and are flagged
	in Table~\ref{tab:thetable}.
	One membership, of TIC~397791443 in IC\,2602, was made manually
	from a literature search
	\citep[e.g.][]{2020A&A...633A..99C}.}  
The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  
The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality and youth of that group.  The yield
in Sco-Cen is not surprising, since Sco-Cen contains the majority of
pre-main-sequence stars in the solar neighborhood, any many of its stars
were selected for TESS 120-second cadence observations by various
guest investigators.  Given the
$\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there may
be many more CQVs in Sco-Cen that remain to be discovered.

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Bonafide, candidate, and debunked complex quasiperiodic
  variables from the TESS 2-minute data. {\bf For internal
  review, full versions are available here
  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
%\toprule
%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
%\midrule
%\endhead
\startdata
TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
-- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
  flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
  \ndebunked\ impostors (\texttt{Quality} flag -1).  The
  machine-readable version, available online, includes additional
  columns for the Gaia DR2 source identifiers and parameter
  uncertainties.  The age uncertainties are typically $\approx \pm
  10\%$, but can be asymmetric.  {\bf The median temperature, radius, and
  mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\%
  respectively}.  $N_{\rm sector}$ denotes the number of TESS sectors
  for which {\it any} data are expected to be acquired between July~2018 and
  Oct~2024.  This number is generally greater than the number of
  sectors for which 120-second cadence data exist.   Association names
  and provenance follow conventions adopted by
  \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	%APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
	The ``(?)'' string denotes low-confidence membership.
}
\end{deluxetable}
\clearpage
